\section{Reproducibility and Artifact Identity}

The release record binds source, containers, model material, workload, raw
measurements, telemetry, and rendered reports. Local Docker image IDs and
unpacked sizes are distinct from registry manifest digests and compressed
sizes; neither is inferred from the other. Native and stock model-artifact
inventories are also recorded independently even though both share the same
repository revision.

\begin{table}[t]
  \centering
  \caption{Digest-bound artifact identity. Registry values not captured by the
  controlled comparison are reported as \texttt{N/A}.}
  \label{tab:artifact-identity}
  \small
  \begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}X}
    \toprule
    Record & Value \\
    \midrule
    Evidence state & \PaperEvidenceState \\
    Native Git commit & \NativeCommit \\
    Stock Git commit & \StockCommit \\
    Native local image ID & \NativeLocalImageId \\
    Native OCI digest & \NativeImageDigest \\
    Stock local image ID & \StockLocalImageId \\
    Stock OCI digest & \StockImageDigest \\
    Shared model revision & \ModelRevision \\
    Native model-artifact evidence SHA-256 & \NativeModelArtifactEvidenceSha \\
    Stock model-artifact evidence SHA-256 & \StockModelArtifactEvidenceSha \\
    Workload SHA-256 & \WorkloadSha \\
    Evidence-manifest SHA-256 & \EvidenceManifestSha \\
    Evidence timestamp & \EvidenceTimestamp \\
    \bottomrule
  \end{tabularx}
\end{table}

The public code location is
\url{https://github.com/luka-loehr/qwen3-tts-native}. The immutable
\href{https://github.com/luka-loehr/qwen3-tts-native/releases/tag/v0.1.0}{v0.1.0
release record} binds the annotated source tag to the exact released OCI
digest and publishes the English LaTeX source, bibliography, vector figures,
generated plot data, final paper PDF, benchmark report PDF, evidence manifest,
and checksums. A registry digest shown as \texttt{N/A} in
Table~\ref{tab:artifact-identity} means that the controlled comparison captured
only the local image identity; it never authorizes deployment by a mutable tag.
Large raw evidence may be hosted separately when the repository cannot carry
it. Any publication record for that bundle is external to schema v1.2 and must
not be inferred from a local path or mutable URL.

Reproduction requires a clean pull by immutable image digest, an idle supported
GPU, the documented hardened run command, a successful full-pipeline readiness
check, and the external workload client. Reproducers should validate the
manifest before generating tables or plots and should report any hardware,
driver, power-mode, workload, or comparator difference rather than presenting
it as the original experiment.
