\section{Streaming API}

The primary endpoint is
\code{POST /v1/voice-design/speech}. A request contains non-empty UTF-8 text, a
natural-language VoiceDesign description, an optional language (default
\code{auto}), an optional seed, a bounded maximum duration, and an output mode.
The endpoint accepts VoiceDesign instructions only; a voice name, speaker
embedding, reference sample, or cloning identifier is not part of the schema.

Progressive responses use \code{multipart/mixed}. The first part is a JSON
start event, subsequent binary parts contain 24,000-Hz mono signed 16-bit
little-endian PCM, and exactly one JSON end or error event terminates the
application stream. Multipart boundaries define application packets; HTTP/1.1
chunks or HTTP/2 DATA frames do not. A separate buffered mode returns a bounded
RIFF/WAVE object after synthesis completes.

The service also exposes liveness, readiness, capability discovery, bounded
request cancellation, and prompt-free Prometheus counters. A conservative
compatibility endpoint returns buffered WAV but is not presented as a complete
implementation of any third-party audio API.

The standalone process does not terminate TLS or implement identity. A public
deployment therefore requires an authenticated and rate-limited proxy with
bounded request and response timeouts. Normal service logs and metrics omit
text, voice descriptions, language values, request identifiers, and generated
audio; surrounding proxies and clients require their own payload-retention
controls.
